### 2020-04-07 manuscript/manuscript.rmd
add burnin and change names for sensitve analyses

### Sensitive test of CAT categories
The major difference between site-heterogeneous CAT and C60 models are the number of substitutional categories that are used in different data matrices. CAT models employ a Dirichlet process prior to infer number of substitutional categories or profiles with different nucleotide or amino acid frequencies to account for substitutional heterogeneity across a phylogenetic data matrix [@Lartillot:2004dq] . Here, we reported the number of categories inferred from CAT model for each PhyloBayes analysis (Table XX). The number of categories is considerable larger than 60 categories used in C60 models, and in most cases even larger than the gene partitions within each data matrix (Table xx). Although the true number of substitutional categories in empirical data matrices is impossible to determine with current phylogenetic tools, we found that the amino frequencies of several categories inferred by C60 model are close to zero from IQtree results, potentially indicating that the C60 models might be already overfitting to most matrices. These results are consistent with the findings that CAT model often overestimate the true number of substitutional categories, especially for large data matrix from simulation analyses [@whelan2016let].

@@

```{r phylogenetic_signal, fig.width=6, fig.height=12}
df2=read_tsv("/animal_root/data_processed/tables/parameters.tsv")
df2$Runs= factor( df2$Runs, levels=c("Poisson_CAT60", "Poisson_CAT70", "Poisson_CAT80", "Poisson_CAT90","Poisson_CAT100","Poisson_CAT110","Poisson_CAT120", "Poisson_CAT150", "Poisson_CAT180", "Poisson_CAT360") )

p<-ggplot(df2, aes(x=Runs, y=Likelihood, group=Topology)) +
    geom_line(aes(color=Topology))+
    geom_point(aes(color=Topology)) + theme(axis.text.x = element_text(angle=45, hjust=1)) + labs(x ="CAT categories", y = "Log-likelihood")
```

>>>>

### Sensitive test of CAT categories {place holder for sensitive results}
The major difference between site-heterogeneous CAT and C60 models are the number of substitutional categories that are used in different data matrices. CAT models employ a Dirichlet process prior to infer number of substitutional categories or profiles with different nucleotide or amino acid frequencies to account for substitutional heterogeneity across a phylogenetic data matrix [@Lartillot:2004dq] . Here, we reported the number of categories inferred from CAT model for each PhyloBayes analysis (Table XX). The number of categories is considerable larger than 60 categories used in C60 models, and in most cases even larger than the gene partitions within each data matrix (Table xx). Although the true number of substitutional categories in empirical data matrices is impossible to determine with current phylogenetic tools, we found that the amino frequencies of several categories inferred by C60 model are close to zero from IQtree results, potentially indicating that the C60 models might be already overfitting to most matrices. These results are consistent with the findings that CAT model often overestimate the true number of substitutional categories, especially for large data matrix from simulation analyses [@whelan2016let].

@@
